\section{Description}

\subsection{Short description}
\paragraph{} We would like to create a website offering guides, tips and
information about student exchanges. The website will provide data sorted by
countries and universities.

\paragraph{} We hope to be able to turn the webiste online by the end of the
year, and provide a stable version during January.

\paragraph{} Not much details about the structure of the website are provided.
Our main task by now will probably to write down a document describing how we
would like to present the website.

\paragraph{} The website will be fed by students.

\paragraph{} Access to the content of the website must be restricted to
students. Further details will be provided in the technical subsection.

\subsection{Technical requirements}

\paragraph{} We must host the website on a server provided by our local student
club. It will probably be a classic LAMP stack (Linux/Apache/Mysql/PHP). We will
not be able to choose to work with an other langage (Ruby, python, ...).

\paragraph{} A Centralized Authentication System (CAS) had been deployed on our
campus. CAS is a standard technology allowing to authenticate user on many
web services using one centralized couple login/password by user. We must use
this platform to grant access to users on the website.

\subsection{Recomandations}

\paragraph{} It has been explicitely asked not to implement a rating or reviews
system, as the teachers don't want the website to contain negative comments from
students.

