\section{Introduction}

\subsection{Project summary}

\paragraph{} At the initiative the Mme Rumpler and the IT department from the
INSA, we would like to design and build a website providing support for exchange
students, including features allowing older students to mentor the ones that are
about to move or currently abroad.

\subsection{Context of the project}

\paragraph{} This project is a scholar assignment realized by a team of
students from France and Germany. At the very least, this project had been set
with the intention of making students discover the specificities of a project on
an international scale. Such a project involves teammates working together from
various locations and speaking different languages. It will obviously imply that
the project organization is adapted to this very specific situation.
Therefore, we must take a special care of a good communication channel between
the two teams.

\paragraph{} This project started on week 42 by kick-off meetings with tutoring
teachers in both schools. The project we are working on is pushed by Mme
Rumpler and the French School (INSA de Lyon). Each stage of the project must be
validated by Mme Rumpler in order to guarantee that the project requirements
are well understood and followed.

\paragraph{} The project agenda sets the last review (and therefore the
deadline) to the second week of January '12. We should have enough time to
build a real-world application that meets the project requirements.
Nevertheless, miscommunication between the two parts of the team is a major risk
of failure.
