\section{Teamates' roles}

\paragraph{} While trying to make a clear list of our respective roles, it
appeared that at the exception of PM and QM, all the teammates will switch from a
role to an other from a step to an other.

\subsection{Project Manager}

\paragraph{} The role of project manager is known of all of us, for the sake of
efficiency, I won't write more about this topic.

\subsection{Quality Manager}

\paragraph{} The quality manager will prepare validation procedures and tools
that we will follow while working on the project and validate the work that is
done according to these procedures.

\paragraph{} Quality Manager work includes listing of points of interest to
check for each step of the project, sometimes document templates and will
prepare tests and Quality Assurance feedback tools.

\subsection{Architect/designer}

\paragraph{} This role includes various tasks. From both technical and
functional side, designers will sketch the website and describe its features.

\paragraph{} The designer will write out the project requirements.

\paragraph{} In order to succeed in its work, the designer will list
best-practices to follow, compare existing websites and technologies that are
meaningful for the project.

\subsection{Developer}

\paragraph{} In this context, the developer will not exactly write a lot of
code. The first job (and not the easiest) of the developer is to discover and
understand the stack of tools the project rely on : from the browser, on client
side to the code framework and APIs from the CMS we'll use, on server side.

\paragraph{} The developer main task will be to set-up and integrate plug-ins
and "modules" to the chosen framework or CMS. The selection of a module depends
on the features it provides, the quality of it's code and it's compatibility
with other modules. The developer will write code for modules when no existing
one statisfies the requirements or has to be updated.

\subsection{Webdesginer/Front-end developer}

\paragraph{} The webdeisgner/Front developer focuses his work on the design and
aspect of the website. We will probably start from an existing template, so the
work of the webdesigner will be to adjust it to our needs.

\paragraph{} This job requires technical skills in HTML/CSS technologies more
than an artistic talent or Photoshop skills.
