\section{Supporting tools we will use}

\subsection{Communication}

\paragraph{} We'll set-up a mailing-list (probably using Google Group, but any
suggestion here is welcome). Excluding video meetings which have a particular
state, the mailing-list is the only official communication platform.

\paragraph{} Video meetings shall be done with Skype and/or Google talk
according to the preference of the majority and technical limitations. In France,
Skype is stupidly considered as potentially harmful because when it had been
launched, it produced a lot of encrypted packets over universities networks.
In a nutshell, Skype can be blocked by a firewall.

\paragraph{} Teammates are free to work and discuss with the tools they want to
use. But these discussions won't be considered as part of the project. For
instance, reviews discussions must most of the time take place via the
mailing-list.

\subsection{Version control}

\paragraph{} I would like to use git and github. It's a Distributed Concurrent
Version System widely used. If you don't know git yet, you'll probably need to
in a near future, so why not discover this tool right now ? The great book "Pro
Git" is available for free (and legally) on the internet.

\paragraph{} Github is a source forge we can use for our project. It provides a
wiki and a ticketing system.

\paragraph{} Documentation can be written in Latex on a git repository or Google
Doc. The later is recommended for the sake of simplicity.

\subsection{Management}

\paragraph{} I think that most of the features a management software (Microsoft
Project, Redmine, etc) would provide are already available with other tools we
will use, except for a Gantt-planing tool, which I (as Project Manager) don't
plan to use.
